The Holy Hand Grenade of Antioch

### 2020-02-19 draft-camelot-holy-grenade.tex
fix: patch source to let latexml parse it

@@

% [NOTE,remove-in-rfc=false]
\begin{note}
  \caption{Spamalot}
  The relevance of the musical "Spamalot" to Internet lore should be
  obvious to the reader; but in case of doubt, see also
  Section 1 ("\textbf{What is Spam?}") of RFC2635.
\end{note}

@@

The participants of that renowned exercise in cross-cultural
communication, to wit the exchange between the
\textit{Knights of the Round Table}
and the taunting French soldiers serving under 
\textbf{Guy de Lombard} are,
properly speaking, outside the scope of this `menagerie`, being more
or less human. Notwithstanding, several^ish^ beasts both animate~d~
and wooden played a significant part in this encounter; most
notably:

@@

The exchange of projectile animals was the beginning of a
long-running fruitful relationship between the British and the
French peoples,
\begin{comment}TODO: Will need to verify that claim.\end{comment} which
arguably predates the traditional English enmity with the
French. [comment]#Strictly speaking, the Knights are Welsh.#

@@

The instructions in the \textit{Book of Armaments} on the proper deployment
of the Holy Hand Grenade of Antioch [bcp14]#may# be summarized as
follows, although this summary \textbf{SHALL NOT} be used as a substitute
for a reading from the Book of Armaments:

@@

  \item Lob the Holy Hand Grenade of Antioch towards the Foe
  \item The Foe, being naughty in the \textbf{LORD's} sight, [bcp14]#shall# snuff it

@@

\begin{longtabu} to \linewidth {|l|l|}

@@

\end{longtabu}

@@

\begin{quote}
&#x2e;כאן אולי ימצאו המילים האחרונות של יוסף מארמתיה
&#x2e;מי אשר יהיה אמיץ ובעל נפש טהורה יוכל למצוא את הגביע הקדוש בטירת אאאאאאאה

"Here may be found the last words of Joseph&nbsp;of Arimathea.
He who is valiant and pure of spirit may find the Holy Grail
in the castle of &mdash; Aaaargh."
\end{quote}

@@

\begin{thebibliography}{1}
\subsection{Normative References}
  \bibitem{RFC2119} 
\end{thebibliography}

\begin{thebibliography}{1}
\subsection{Informative References}

>>>>

%% Temporary fixes %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newenvironment{aside}{}{}
\newenvironment{comment}{}{}
\let\cmt\relax% [comment]#...#
\let\bcp\relax% [bcp14]#...#
\usepackage{verbatim}
\newenvironment{sourcecode}{\verbatim}{\endverbatim}
\usepackage{longtable}
\usepackage{multirow}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% [NOTE,remove-in-rfc=false]
\begin{note}
  % TODO: \caption{Spamalot}
  The relevance of the musical "Spamalot" to Internet lore should be
  obvious to the reader; but in case of doubt, see also
  Section 1 ("\textbf{What is Spam?}") of RFC2635.
\end{note}

@@

The participants of that renowned exercise in cross-cultural
communication, to wit the exchange between the
\textit{Knights of the Round Table}
and the taunting French soldiers serving under 
\textbf{Guy de Lombard} are,
properly speaking, outside the scope of this `menagerie`, being more
% TODO: or less human. Notwithstanding, several^ish^ beasts both animate~d~
and wooden played a significant part in this encounter; most
notably:

@@

The exchange of projectile animals was the beginning of a
long-running fruitful relationship between the British and the
French peoples,
\begin{comment}TODO: Will need to verify that claim.\end{comment} which
arguably predates the traditional English enmity with the
French. \cmt{Strictly speaking, the Knights are Welsh.}

@@

The instructions in the \textit{Book of Armaments} on the proper deployment
of the Holy Hand Grenade of Antioch \bcp{may} be summarized as
follows, although this summary \textbf{SHALL NOT} be used as a substitute
for a reading from the Book of Armaments:

@@

  \item Lob the Holy Hand Grenade of Antioch towards the Foe
  \item The Foe, being naughty in the \textbf{LORD's} sight, \bcp{shall} snuff it

@@

% \begin{longtabu} to \linewidth {|l|l|}
\begin{longtable}{|l|l|}

@@

\end{longtable}
% \end{longtabu}

@@

\begin{quote}
.כאן אולי ימצאו המילים האחרונות של יוסף מארמתיה
.מי אשר יהיה אמיץ ובעל נפש טהורה יוכל למצוא את הגביע הקדוש בטירת אאאאאאאה

"Here may be found the last words of Joseph~of Arimathea.
He who is valiant and pure of spirit may find the Holy Grail
in the castle of --- Aaaargh."
\end{quote}

@@

\subsection{Normative References}
\begin{thebibliography}{1}
  \bibitem{RFC2119} 
\end{thebibliography}

\subsection{Informative References}
\begin{thebibliography}{1}
